Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-06 pecomplexity.tex
Adding cleaning up Figures

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{amsthm}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/SVD1RegimesColored}\caption{SVD IPC Time Series with Regimes Colored}
\label{default}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/full}\caption{SVD IPC Full Time Series}
\label{default}
\end{center}
\end{figure}

>>>>

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdipcfull}
                \caption{SVD IPC without coloring}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdipcregimescolored}
                \caption{SVD IPC with coloring}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Full Time Series }\label{fig:svdFull}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colfullts}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colshortts}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{col  Time Series }\label{fig:svdFull}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/gccfullts}\caption{403.gcc full time series}
\label{default}
\end{center}
\end{figure}

@@
